---
title: "Linreg Vignette"
author: Maxime Bonneau, Niclas Lovsjö
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linreg Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
library(lab4bis)
library(ggplot2)
library(gridExtra)
```

##Description
Linreg is a package that performs linear regression. It takes a *formula* of the form *Y~**X***, where **X** and **Y** are vector-valued, and a *data-frame* from which we can take the values of **Y** and **X**. 

### Attributes:
The function *Linreg* returns a list of the class *Linreg*, having the elements: coefficients, resid, df.residual,rank, call, fitted.values, rstudent. 

### Methods:   
  *     resid(X):    
             Gives the residuals as a vector.  
  *     pred(X, Z):    
        Gives the predicted values of the linear model X for the values of the variable Z.  
  *     print(X):  
        Returns the called formula and the estimate of the coefficients.  
  *     plot(X):  
        Plots the Residuals vs. fitted values and Scale-location.  
  *     coef(X):  
        Returns a named vector of the estimate of the coefficients.  

### Example
```{r}
our_linear_regression <- linreg(Petal.Length~Sepal.Length,iris)
print(our_linear_regression)
```


```{r}
plot(our_linear_regression)
```

```{r}
coef(our_linear_regression)
```

```{r}
resid(our_linear_regression)
```

```{r}

pred(our_linear_regression, 2)
```


> "He who uses linreg, might just as well use lm ~ Unknown thinker"


